Goes Here

### 2012-07-31 paper.tex
add more figures

A plot of bounce height after each iteration.

Loaded dice. It has a certain probability to land on "1".
A table of probability distribution of landing on each side
is shown in Table~\ref{tab:dice}.

>>>>

A plot of bounce height after each iteration.
The height and desired height is plotted in Figure~\ref{fig:ball}
\begin{figure}
	\centering
 	\includegraphics[width=0.3\textwidth]{figure/ballHeight.pdf}
\caption{Simulated height per-iteration of a ball bouncing after free-falling at 1 meter height.
	Redline is desired height.}
\label{fig:ball}
\end{figure}

A loaded die as shown in Figure~\ref{fig:die}. 
\begin{figure}
	\centering
 	\includegraphics[width=0.25\textwidth]{figure/die.png}
\caption{A printed loaded die}
\label{fig:die}
\end{figure}
It has a certain probability to land on "1".
A table of probability distribution of landing on each side
is shown in Table~\ref{tab:dice}.
